On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-04-01 docs/mvfits_paper/mvf.tex
Reorder role of remnant quantities sentance [21]

\par Both Phenom and \eob{} approaches either use phenomenological models of remnant \bh{} mass and spin to interpolate over tables of \qnm{} frequencies, or phenomenological models for \qnm{} frequencies are used directly.

>>>>

\par Phenomenological models of remnant \bh{} mass and spin are used by both Phenom and \eob{} approaches either to interpolate over tables of \qnm{} frequencies or in the evaluation of phenomenological models for \qnm{} frequencies.
